Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-04 paper/paper.tex
+details on the synthesis spec

\paragraph{Running example synthesis}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
Our goal is to synthesise ...
% Counterexample from first cruisecontrol02.c benchmark with uncertainty and
% nondeterminism:
% 1) { (0.02634525299072265625, 0.9979267120361328125, -0.99768829345703125) }
% 2) { (0.02644824981689453125, 1.00053310394287109375, -1.0014629364013671875) }

>>>>

\paragraph{Running example synthesis}

There are two different algorithms in DSVerifier that can be used for
stability verification, one based on Schur's decomposition and another
one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16};
here, the Jury's method is chosen due to its efficiency.

Jury's algorithm is used to check the stability in the $z$-domain
for a given characteristic polynomial of the form:
%
$$
S(z) = a_0Z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
$$
%
For the stability test procedure, the following Jury matrix
$M = [m_{ij}]_{(2N−2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right)
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \texttt{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\texttt{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
\end{array}
\right.
$$
%
where $k \in \mathbb{Z}$, such that $0 < k < N − 2$. 
$S(z)$ is the
characteristic polynomial of a stable system if and only if
the following four propositions hold:
\begin{itemize}
\item $R_1: S(1) > 0$;
\item $R_2: (−1)^N S(−1) > 0$;
\item $R_3: |a_0| < a_N$;
\item $R_4: m_{11} > 0 \equiv m_{31} \wedge m_{51} \wedge \cdots \wedge m_{(2N−3)(1)}$.
\end{itemize}

The stability property is then encoded by creating a
constraint of the form:
$$\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4)$$
\cdsay{figure out what is existentially quantified for the final $\sigma$.}

We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
Our goal is to synthesise ...
% Counterexample from first cruisecontrol02.c benchmark with uncertainty and
% nondeterminism:
% 1) { (0.02634525299072265625, 0.9979267120361328125, -0.99768829345703125) }
% 2) { (0.02644824981689453125, 1.00053310394287109375, -1.0014629364013671875) }
